\vspace*{-0.25cm}
\cvsection{Experience}
\vspace*{-0.25cm}
\begin{cventries}
  
  \cventry
    {Undergraduate Researcher (Prof. Michael Miller)}
    {National Center for Supercomputing Applications (NCSA) }
    {Urbana, IL}
    {May. 2018 - July. 2018}
    {
      \begin{cvitems}
        \item {Worked on a speech to text auto captioning service and classifiers using open source captioning APIs and machine learning.}
        \item {This project researches frameworks and workflows for speech-to-text recognition in order to facilitate live auto captioning and creation of standard caption files for use in live events and video editing, utilizing and enhancing speech-to-text HPC/cloud services and seeks to advance the state of the art in speech-to-text recognition.}
      \end{cvitems}
      \vspace*{-0.25cm}
    }
    
  \cventry
    {Course Assistant for CS 125 Spring 2018}
    {Undergraduate Course Assistant}
    {Urbana, IL}
    {Jan. 2018 - May. 2018}
    {
      \begin{cvitems}
        \item {Assisted students in labs about Introductory computer science concepts, Object Oriented Programming (Java), basic data structures and Recursion.}
        \item {Was involved in office hours where I helped students with weekly homework assignments.}
      \end{cvitems}
    }
    
\end{cventries}
\vspace*{0.15cm}
\cvsection{Leadership Positions}
\vspace*{-0.25cm}
\begin{cventries}
  \cventry
    {Experience Staff}
    {HackIllinois}
    {Urbana, IL}
    {Sep. 2017- current}
    {
      \begin{cvitems}
        \item {Worked in planning out the hackers' experience at the event.}
        \item {Determining the criteria for accepting hackers in the event. Worked with mentors and sponsors to organize workshops.}
        \item {Planning the layout of all the events and workshops as well as planning out logistics of the event.}
      \end{cvitems}
      \vspace*{-0.4cm}
    }
  \cventry
    {Website Staff}
    {Reflections | Projections}
    {Urbana, IL}
    {Jan. 2018 - current}
    {
      \begin{cvitems}
        \item {On the website development team for the largest student run technology conference in the Midwest.}
        \item {Worked with a team on building the website for mentors and the landing page for students.}
      \end{cvitems}
    }
    \cventry
    {Teacher}
    { Sail CS@Illinois}
    {Urbana, IL}
    {April 2018}
    {
        \begin{cvitems}
            \item {One the teachers for the annual event which aims to teach Computer Science Courses to High School Students for getting them involved in CS.}
            \item {Taught students basics of Recursion, Memoization, Graph-Traversal and Searching algorithms in the course "Recursion for dummies"}
        \end{cvitems}
        \vspace*{0.55cm}
    }
\end{cventries}
