\cvsection{Projects}
\begin{cventries}
  \cventry
    {Chrome Extension}
    {Partial}
    {Urbana, IL}
    {Sep. 2017}
    {
        \begin{cvitems}
          \item {Building a Chrome extension using open source Python natural language processing libraries and APIs (Currently using Watson and Vader apis, but we want to train our own model for future uses) to perform sentiment analysis in order to determine the level of bias present in a news article.}
          \item {Working with a project team to create a Javascript front end and Python backend deployed on Heroku.}
          \end{cvitems}
          \vspace*{-0.25cm}
    }
    \cventry
    {Android Application}
    {Go Get Out}
    {Urbana, IL}
    {Sep. 2017}
    {
        \begin{cvitems}
          \item {A fitness application for motivating lazy people to go get out! Go for a jog or a run by finding a workout buddy with same exercise preferences in your proximity.}
          \item {Used Firebase to store data and Google Maps api to get current location and display path and maps activity. Source code on personal website.}
          \end{cvitems}
          \vspace*{0.45cm}
    }
    \cventry
    {Voice controlled small talk chatbot}
    {Small Talk Boy}
    {Urbana, IL}
    {Mar. 2018}
    {
        \begin{cvitems}
          \item {A chat bot with small talk onversation skills.}
          \item {Uses speech recognition and sentiment analysis to provide short responses to generic small talk. Uses Watson and Diagflow for sentiment analysis and speech recognition.}
          \end{cvitems}
          \vspace*{0.45cm}
    }
    \cventry
    {Side projects done while playing around with open source APIs}
    {Github projects}
    {Urbana, IL}
    {Sep. 2017}
    {
        \begin{cvitems}
          \item {I spend a lot of time tweaking with open source APIs and try to incorporate them in fun programs. Some of them are, voice controlled text based rpg in java, tfidf and sentiment analysis on nursery rhymes, a naive bayes classifier that I wrote and many more on \url{github.com/itsmesatwik}.}
          \end{cvitems}
    }
\end{cventries}
